Clicks and Cliques

### 2018-12-27 papersoul.Rnw
fix econ chunk labels

<<moving, dependson='data', echo=FALSE,results='asis', cache=FALSE>>=
soul %>% 
  mutate(Q5 = recode_factor(Q5, "(DK)" = "Non Response", 
    "(Refused)" = "Non Response",
    "Move outside of (answer from Sc) but stay in the state" = "Move from your neighborhood",
    "Move outside of this communitybut stay in the state" = "Move from your neighborhood",
    "Move to another city and state altogether" = "Move from your neighborhood",
    "Move to another neighborhood in (answer from Sc)" = "Move from your neighborhood", 
    "Move to another neighborhood in this community" = "Move from your neighborhood")) %>%  
  filter(!is.na(PROJWT)) %>% 
  mutate(pr = PROJWT/3)  %>% 
  svydesign(ids =~1, strata =~QSB, weights =~pr, data = .) %>% 
  svyby(~Q5,~CCEGRP2, design = ., svymean,keep.var = FALSE, na.rm = T) %>% 
  ftable() %>% data.frame() %>% mutate(Freq = Freq*100) %>% 
  mutate( Var2 = gsub('statistic.Q5', '', Var2) ) %>% 
  spread(CCEGRP2, Freq) %>%  
  xtable(caption = 'Willingness to move outside your neighborhood', label = 'move') %>% 
  print(caption.placement = 'top')

@@

The bottom panel of Figure \ref{eco} presents the U.S. GDP growth rate in 2008, 2009, and 2010. A similar pattern is observed in both panels, suggesting the economic dimension is less related with attachment during the economic crisis.
\begin{figure}[hbpt]
<<econ, dependson=c('data'), echo=FALSE,message=FALSE,warning=FALSE, fig.height=4>>=
svydesign(ids =~ 1, strata =~ QSB, weights =~ PROJWT, data = filter(soul,!is.na(PROJWT))) %>% 
  svyby( ~ ECONOMY + CCE, ~ YEAR, design = ., svyvar, keep.var = TRUE, na.rm = T)  %>% data.frame() %>% select(1:5) %>% 
  mutate(rho = V2/sqrt(V1*V4), gdp = c(-0.4,-3.5,3.0)) %>% 
  gather(variable, value,rho,gdp) %>% 
  select(YEAR, variable, value) %>% 
  mutate(variable =  factor(variable, labels = c('Attachment-Economy correlation', 'GDP Rate')
)) %>% ggplot(aes(x = YEAR, y = value)) + 
  geom_line() + geom_point() +
  labs(x = "", y = "", 
       title = 'Evolution of Attachment-Economy correlation and GDP') +
  facet_grid(facets = variable~., scales = 'free') + 
  ggtitle('Evolution of Attachment-Economy correlation and GDP')

# des.wt.year <- svydesign(ids =~ 1, strata =~ QSB, weights =~ PROJWT, data = filter(soul,!is.na(PROJWT)))
# vars  <- svyby( ~ ECONOMY + CCE, ~ YEAR, des.wt.year, svyvar, keep.var = TRUE, na.rm = T)
# vars <- mutate(vars[, 1:5], rho = with(vars, V2/sqrt(V1*V4)), gdp = c(-0.4,-3.5,3.0))
# 
# rhos.m <- gather(vars, variable, value,rho,gdp) %>%
#   select(YEAR, variable, value) %>%
#   mutate(variable =  factor(variable, labels = c('Attachment-Economy correlation', 'GDP Rate')
# ))
# 
# ggplot(data = rhos.m, aes(x = YEAR, y = value)) +
#   labs(x = "", y = "", title = 'Evolution of Attachment-Economy correlation and GDP') +
#   geom_line() + geom_point() +
#   facet_grid(facets = variable~., scales = 'free') +
#   ggtitle('Evolution of Attachment-Economy correlation and GDP')

@
\caption{Attachment vs economic dimension. Top panel shows the correlation between attachment and economy index against time. Bottom panel shows the GDP growth rate against years. \label{eco}}
\end{figure}

>>>>

<<moving, dependson='data', echo=FALSE,results='asis', cache=FALSE>>=
soul %>% 
  mutate(Q5 = recode_factor(Q5, "(DK)" = "Non Response", 
    "(Refused)" = "Non Response",
    "Move outside of (answer from Sc) but stay in the state" = "Move from your neighborhood",
    "Move outside of this communitybut stay in the state" = "Move from your neighborhood",
    "Move to another city and state altogether" = "Move from your neighborhood",
    "Move to another neighborhood in (answer from Sc)" = "Move from your neighborhood", 
    "Move to another neighborhood in this community" = "Move from your neighborhood")) %>%  
  filter(!is.na(PROJWT)) %>% 
  mutate(pr = PROJWT/3)  %>% 
  svydesign(ids =~1, strata =~QSB, weights =~pr, data = .) %>% 
  svyby(~Q5,~CCEGRP2, design = ., svymean,keep.var = FALSE, na.rm = T) %>% 
  ftable() %>% data.frame() %>% mutate(Freq = Freq*100) %>% 
  mutate( Var2 = gsub('statistic.Q5', '', Var2) ) %>% 
  spread(CCEGRP2, Freq) %>%  
  xtable(caption = 'Willingness to move outside your neighborhood', label = 'move') %>% 
  print(caption.placement = 'top', include.rownames=FALSE)

@@

The bottom panel of Figure \ref{eco} presents the U.S. GDP growth rate in 2008, 2009, and 2010. A similar pattern is observed in both panels, suggesting the economic dimension is less related with attachment during the economic crisis.
\begin{figure}[hbpt]
<<econ, dependson=c('data'), echo=FALSE,message=FALSE,warning=FALSE, fig.height=5>>=
svydesign(ids =~ 1, strata =~ QSB, weights =~ PROJWT, data = filter(soul,!is.na(PROJWT))) %>% 
  svyby( ~ ECONOMY + CCE, ~ YEAR, design = ., svyvar, keep.var = TRUE, na.rm = T)  %>% data.frame() %>% select(1:5) %>% 
  mutate(rho = V2/sqrt(V1*V4), gdp = c(-0.4,-3.5,3.0)) %>% 
  gather(variable, value,rho,gdp) %>% 
  select(YEAR, variable, value) %>% 
  mutate(variable =  factor(variable, labels = c('GDP Rate','Attachment-Economy correlation'))) %>% ggplot(aes(x = YEAR, y = value)) + 
  geom_line() + geom_point() +
  labs(x = "", y = "", 
       title = 'Evolution of Attachment-Economy correlation and GDP') +
  facet_grid(facets = variable~., scales = 'free') + 
  ggtitle('Evolution of Attachment-Economy correlation and GDP')

@
\caption{Attachment vs economic dimension. Top panel shows the correlation between attachment and economy index against time. Bottom panel shows the GDP growth rate against years. \label{eco}}
\end{figure}
\newpage
